---
title: "Mixtures Bioactivity: Exposure Ratio Case Study"
author: "Rachel Broughton"
date: "2025-04-09"
output: html_document
---

## Setup Environment
```{r}
# clear variables
rm(list = ls())

library(tcplfit2)
library(tcpl)
library(dplyr)
library(ggplot2)
library(plotly)
library(haven)
library(survey)
library(rootSolve)
library(reshape2)
library(scales)
library(latex2exp)
library(gridExtra)
library(cowplot)

# tcpl database connection
tcplConf("_dataminer", pass="pass", db="invitrodb", drvr="MySQL", host="ccte-mysql-res.dmap-prod.aws.epa.gov")
tcplConfList()

source("./scripts/mixture_model_functions.R")
```

## Load data from NHANES files 
Load all PFAS chemicals tested by NHANES and select which ones to examine
'PFC_F.xpt' and 'DEMO_F.xpt' files are from NHANES and were accessed from:
https://wwwn.cdc.gov/nchs/nhanes/continuousnhanes/default.aspx?BeginYear=2009

```{r}
# read in NHANES 2009-2010 sample C data
demo2009_sampleC <- read_xpt("./input/PFC_F.XPT")
# read in information that relates NHANES chemical identifiers to DTXSIDs
pfas_chems <- read.csv("./input/pfas.csv")
# remove rows with NA values to eliminate subjects in sample C who were not tested for all of these chemicals
# 199/2432 subjects have missing data for these chemicals = 8.18%. Less than the 10%, which is the accepted amount that can be ignored with no adjustments to the weights in the NHANES Analytic Guidelines
# https://wwwn.cdc.gov/nchs/data/nhanes/analyticguidelines/99-10-analytic-guidelines.pdf
# https://wwwn.cdc.gov/nchs/nhanes/analyticguidelines.aspx
sampleC <- na.omit(demo2009_sampleC)
# change below limit of detection to zero
sampleC_limit <- ifelse(sampleC[,4]==1,sampleC[,3]<- 0,sampleC[,3] <- sampleC[,3])

# Remove the 3 chemicals not tested in the ToxCast chemical library:DTXSID8031861, DTXSID10624392,DTXSID5062760
dtxsids_all <- pfas_chems$DSSTox_Substance_Id[!pfas_chems$DSSTox_Substance_Id %in% c('DTXSID8031861', 
                                                                                 'DTXSID10624392',
                                                                                 'DTXSID5062760')]
# check if any chemicals have more than 25% of data below the limit of detection
below_lld_test <- data.frame(dtxsid=dtxsids_all,lld_frac=NA)
for(jj in 1:length(dtxsids_all)){
  chem_id <- pfas_chems$external_id[pfas_chems$DSSTox_Substance_Id==dtxsids_all[jj]]
  lld_frac <- sum(demo2009_sampleC[,which(colnames(demo2009_sampleC)==chem_id)+1],na.rm=TRUE)/sum(!is.na(demo2009_sampleC[,which(colnames(demo2009_sampleC)==chem_id)]))
  below_lld_test$lld_frac[jj] <- lld_frac
}
# remove chemicals with more than 25% of data below the limit of detection
dtxsids <- dtxsids_all[below_lld_test$lld_frac <= 0.25]
# also remove PFDA because has very discrete measurements at lower concentration levels
dtxsids <- dtxsids[2:5]
# 4 PFAS chemicals tested in NHANES blood serum samples and in the legacy ToxCast chemical library remain and are able to be used for analysis

# create all combinations of the 4 PFAS chemicals
pfas_combos_2 <- data.frame(t(combn(dtxsids,2)),X3=NA,X4=NA)
pfas_combos_3 <- data.frame(t(combn(dtxsids,3)),X4=NA)
pfas_combos_4 <- data.frame(t(combn(dtxsids,4)))
pfas_combos <- data.frame(rbind(pfas_combos_2,pfas_combos_3,pfas_combos_4))
pfas_combos$mix_num <- c(1:nrow(pfas_combos))

pfas_combos$mix_concs <- NA
# make a dataframe with all subjects for each chemical combo
# contains sample SEQN number, measured individual chemical and total mixture concentrations in micro-moles/L [uM],
# and concentration fractions of each component in the mixture
# 2 chemicals
for (ii in 1:6){
  chem_id_1 <- pfas_chems$external_id[pfas_chems$DSSTox_Substance_Id==pfas_combos$X1[ii]]
  chem_id_2 <- pfas_chems$external_id[pfas_chems$DSSTox_Substance_Id==pfas_combos$X2[ii]]
  mw1 <- pfas_chems$Structure_MolWt[pfas_chems$DSSTox_Substance_Id==pfas_combos$X1[ii]]
  mw2 <- pfas_chems$Structure_MolWt[pfas_chems$DSSTox_Substance_Id==pfas_combos$X2[ii]]

  temp <- data.frame(SEQN=sampleC$SEQN,
                     chem1_conc=sampleC[[chem_id_1]]/mw1,
                     chem2_conc=sampleC[[chem_id_2]]/mw2)
  temp$cM_tot <- temp$chem1_conc + temp$chem2_conc
  temp$cfrac_1 <- temp$chem1_conc/temp$cM_tot
  temp$cfrac_2 <- temp$chem2_conc/temp$cM_tot
  pfas_combos$mix_concs[ii] <- list(temp)
}
# 3 chemicals
for (ii in 7:10){
  chem_id_1 <- pfas_chems$external_id[pfas_chems$DSSTox_Substance_Id==pfas_combos$X1[ii]]
  chem_id_2 <- pfas_chems$external_id[pfas_chems$DSSTox_Substance_Id==pfas_combos$X2[ii]]
  chem_id_3 <- pfas_chems$external_id[pfas_chems$DSSTox_Substance_Id==pfas_combos$X3[ii]]
  mw1 <- pfas_chems$Structure_MolWt[pfas_chems$DSSTox_Substance_Id==pfas_combos$X1[ii]]
  mw2 <- pfas_chems$Structure_MolWt[pfas_chems$DSSTox_Substance_Id==pfas_combos$X2[ii]]
  mw3 <- pfas_chems$Structure_MolWt[pfas_chems$DSSTox_Substance_Id==pfas_combos$X3[ii]]
  temp <- data.frame(SEQN=sampleC$SEQN,
                     chem1_conc=sampleC[[chem_id_1]]/mw1,
                     chem2_conc=sampleC[[chem_id_2]]/mw2,
                     chem3_conc=sampleC[[chem_id_3]]/mw3)
  temp$cM_tot <- temp$chem1_conc + temp$chem2_conc + temp$chem3_conc
  temp$cfrac_1 <- temp$chem1_conc/temp$cM_tot
  temp$cfrac_2 <- temp$chem2_conc/temp$cM_tot
  temp$cfrac_3 <- temp$chem3_conc/temp$cM_tot
  pfas_combos$mix_concs[ii] <- list(temp)
}
# 4 chemicals
ii <- 11
chem_id_1 <- pfas_chems$external_id[pfas_chems$DSSTox_Substance_Id==pfas_combos$X1[ii]]
chem_id_2 <- pfas_chems$external_id[pfas_chems$DSSTox_Substance_Id==pfas_combos$X2[ii]]
chem_id_3 <- pfas_chems$external_id[pfas_chems$DSSTox_Substance_Id==pfas_combos$X3[ii]]
chem_id_4 <- pfas_chems$external_id[pfas_chems$DSSTox_Substance_Id==pfas_combos$X4[ii]]
mw1 <- pfas_chems$Structure_MolWt[pfas_chems$DSSTox_Substance_Id==pfas_combos$X1[ii]]
mw2 <- pfas_chems$Structure_MolWt[pfas_chems$DSSTox_Substance_Id==pfas_combos$X2[ii]]
mw3 <- pfas_chems$Structure_MolWt[pfas_chems$DSSTox_Substance_Id==pfas_combos$X3[ii]]
mw4 <- pfas_chems$Structure_MolWt[pfas_chems$DSSTox_Substance_Id==pfas_combos$X4[ii]]
temp <- data.frame(SEQN=sampleC$SEQN,
                   chem1_conc=sampleC[[chem_id_1]]/mw1,
                   chem2_conc=sampleC[[chem_id_2]]/mw2,
                   chem3_conc=sampleC[[chem_id_3]]/mw3,
                   chem4_conc=sampleC[[chem_id_4]]/mw4)
temp$cM_tot <- temp$chem1_conc + temp$chem2_conc + temp$chem3_conc + temp$chem4_conc
temp$cfrac_1 <- temp$chem1_conc/temp$cM_tot
temp$cfrac_2 <- temp$chem2_conc/temp$cM_tot
temp$cfrac_3 <- temp$chem3_conc/temp$cM_tot
temp$cfrac_4 <- temp$chem4_conc/temp$cM_tot
pfas_combos$mix_concs[ii] <- list(temp)
```

## Load chemical data from ToxCast
Select endpoints for analysis of all chemicals and pull data from ToxCast
```{r}
# select 3 enpoints for analysis: ATG_PPRE_CIS, ATG_PPARa_TRANS, ATG_PPARg_TRANS
mc5_aeids <- c(102,132,134)
# mc5_aeids <- c(97,134)
mc5_all <- tcplPrepOtpt(tcplLoadData(lvl = 5, fld = "aeid", val = mc5_aeids))
# subset to get one per chemical
mc5 <- tcplSubsetChid(tcplPrepOtpt(tcplLoadData(lvl = 5, fld = "aeid", val = mc5_aeids)))
mc5_filter <- subset(mc5,dsstox_substance_id %in% dtxsids)
  
norm_factor_102 <- max(subset(mc5_all, aeid ==102)$top, na.rm=TRUE)
norm_factor_132 <- max(subset(mc5_all, aeid ==132)$top, na.rm=TRUE)
norm_factor_134 <- max(subset(mc5_all, aeid ==134)$top, na.rm=TRUE)

mc5_mix_102 <- subset(mc5_filter,aeid==102)
mc5_mix_132 <- subset(mc5_filter,aeid==132)
mc5_mix_134 <- subset(mc5_filter,aeid==134)

```

## Choose one endpoint for analysis
```{r}
# select one endpoint to analyze at a time
mc5_data <- mc5_mix_132
norm_factor <- norm_factor_132
# load other levels for selected endpoint
mc3 <- tcplPrepOtpt(tcplLoadData(lvl = 3, type="mc", fld = "aeid", val = c(132)))
mc4 <- tcplPrepOtpt(tcplLoadData(lvl = 4, type="mc", fld = "aeid", val = c(132)))
mc4_agg <- tcplPrepOtpt(tcplLoadData(lvl = "agg", type="mc", fld = "aeid", val = c(132)))
```

## Compute mixture ACC
Compute the activity concentration at the cutoff as the point of departure using the concentration addition model for all the mixtures
```{r}
# 2 chemicals
pfas_combos$results <- NA
for (ii in c(1:6)){
  comp1 <- mc5_data %>% filter(dsstox_substance_id == pfas_combos$X1[ii])
  comp2 <- mc5_data %>% filter(dsstox_substance_id == pfas_combos$X2[ii])
  comps <- rbind(comp1,comp2)
  cfracs <- cbind(pfas_combos$mix_concs[[ii]]$cfrac_1,pfas_combos$mix_concs[[ii]]$cfrac_2)
  acc_ca <- apply(cfracs,1,ca_point_conc_multi,YY=comps$coff[1],comps=comps)
  # Compute bioactivity:exposure ratio
  ber <- acc_ca/pfas_combos$mix_concs[[ii]]$cM_tot
  # Save in data frame
  pfas_combos$results[ii] <- list(data.frame(pfas_combos$mix_concs[[ii]],
                                             acc_ca=acc_ca,
                                             ber=ber))
}

# 3 chemicals
for (ii in c(7:10)){
  comp1 <- mc5_data %>% filter(dsstox_substance_id == pfas_combos$X1[ii])
  comp2 <- mc5_data %>% filter(dsstox_substance_id == pfas_combos$X2[ii])
  comp3 <- mc5_data %>% filter(dsstox_substance_id == pfas_combos$X3[ii])
  comps <- rbind(comp1,comp2,comp3)
  cfracs <- cbind(pfas_combos$mix_concs[[ii]]$cfrac_1,pfas_combos$mix_concs[[ii]]$cfrac_2,pfas_combos$mix_concs[[ii]]$cfrac_3)
  acc_ca <- apply(cfracs,1,ca_point_conc_multi,YY=comps$coff[1],comps=comps)
  # Compute bioactivity:exposure ratio
  ber <- acc_ca/pfas_combos$mix_concs[[ii]]$cM_tot
  pfas_combos$results[ii] <- list(data.frame(pfas_combos$mix_concs[[ii]],
                                             acc_ca=acc_ca,
                                             ber=ber))
}

# 4 chemicals
ii <- 11
comp1 <- mc5_data %>% filter(dsstox_substance_id == pfas_combos$X1[ii])
comp2 <- mc5_data %>% filter(dsstox_substance_id == pfas_combos$X2[ii])
comp3 <- mc5_data %>% filter(dsstox_substance_id == pfas_combos$X3[ii])
comp4 <- mc5_data %>% filter(dsstox_substance_id == pfas_combos$X4[ii])
comps <- rbind(comp1,comp2,comp3,comp4)
cfracs <- cbind(pfas_combos$mix_concs[[ii]]$cfrac_1,pfas_combos$mix_concs[[ii]]$cfrac_2,
                pfas_combos$mix_concs[[ii]]$cfrac_3,pfas_combos$mix_concs[[ii]]$cfrac_4)
acc_ca <- apply(cfracs,1,ca_point_conc_multi,YY=comps$coff[1],comps=comps)
# Compute bioactivity:exposure ratio
ber <- acc_ca/pfas_combos$mix_concs[[ii]]$cM_tot
pfas_combos$results[ii] <- list(data.frame(pfas_combos$mix_concs[[ii]],
                                           acc_ca=acc_ca,
                                           ber=ber))
```

## Get data for single chemicals
Get single chemical ACC and BER values and analyze by survey demographics
```{r}
# match single chemicals
pfas_single <- data.frame(dtsxid=mc5_mix_132$dsstox_substance_id,acc=mc5_data$acc)
for (ii in 1:nrow(pfas_single)){
  chem_id <- pfas_chems$external_id[pfas_chems$DSSTox_Substance_Id==pfas_single$dtsxid[ii]]
  mw <- pfas_chems$Structure_MolWt[pfas_chems$DSSTox_Substance_Id==pfas_single$dtsxid[ii]]
  ber <- pfas_single$acc[ii]/(sampleC[[chem_id]]/mw)
  pfas_single$exposure[ii] <- list(data.frame(SEQN=sampleC$SEQN,
                                          exp_conc=(sampleC[[chem_id]])/mw,
                                          ber=ber))
}

# Summarize lower limits of detection for each chemical
llod_uM <- c(0.000249931,0.000176694,0.000241505,0.000399896)

for (ii in 1:nrow(pfas_single)){
  #Demographic data for 2009-2010 data
  demo2009 <- read_xpt("./input/DEMO_F.XPT")
  demo2009_wts <- read_xpt("./input/PFC_F.XPT")
  nhanes_vars_c <- demo2009_wts %>% select(SEQN, WTSC2YR)
  nhanes_vars <- demo2009 %>% select(SEQN,SDMVPSU,SDMVSTRA,RIAGENDR,RIDAGEYR,RIDRETH1,INDFMPIR)
  test_df <- merge(pfas_single$exposure[[ii]],nhanes_vars,by="SEQN")
  pfas_mix_demo <- merge(test_df,nhanes_vars_c,by="SEQN")
  # convert gender to factor
  pfas_mix_demo <- pfas_mix_demo %>%
                      mutate(RIAGENDR = recode(RIAGENDR, `1` = 0L,`2` = 1L))
  pfas_mix_demo$RIAGENDR <- as.factor(pfas_mix_demo$RIAGENDR)
  # convert age to factor
  # seperate below 20 and above 20
  pfas_mix_demo <- pfas_mix_demo %>% mutate(age_group = ifelse(RIDAGEYR < 20, 0L, 1L))
  pfas_mix_demo$age_group <- as.factor(pfas_mix_demo$age_group)
  # convert ratio of family income to poverty to factor
  pfas_mix_demo <- pfas_mix_demo %>% mutate(income_group = ifelse(INDFMPIR<5, 1L, INDFMPIR))
  pfas_mix_demo <- pfas_mix_demo %>% mutate(income_group = ifelse(INDFMPIR==5, 2L, income_group))
  pfas_mix_demo <- pfas_mix_demo %>% mutate(income_group = ifelse(is.na(INDFMPIR), 0L, income_group))
  # use survey package to apply nhanes weights
  nhanes_design <- svydesign(id = ~SDMVPSU,
                             strata = ~SDMVSTRA,
                             weights = ~WTSC2YR,
                             nest = TRUE,
                             data = pfas_mix_demo)
  # evaluate by whole population median
  pop_med <- svyquantile(~ber, design = nhanes_design, quantile=c(0.5), ci=TRUE)
 # evaluate mediants based on survey demographic groups
  gender_med <- svyby(~ber, ~RIAGENDR,design=nhanes_design,svyquantile,quantile=c(0.5), ci=TRUE)
  age_med <- svyby(~ber, ~age_group,design=nhanes_design,svyquantile,quantile=c(0.5), ci=TRUE)
  race_med <- svyby(~ber, ~RIDRETH1,design=nhanes_design,svyquantile,quantile=c(0.5), ci=TRUE)
  income_med <- svyby(~ber, ~income_group,design=nhanes_design,svyquantile,quantile=c(0.5), ci=TRUE)

  pfas_single$popmed[ii] <- pop_med$ber[1]
  pfas_single$malemed[ii] <- gender_med$ber[1]
  pfas_single$femmed[ii] <- gender_med$ber[2]
  pfas_single$youngmed[ii] <- age_med$ber[1]
  pfas_single$oldmed[ii] <- age_med$ber[2]
  pfas_single$mexamer[ii] <- race_med$ber[1]
  pfas_single$hispanic[ii] <- race_med$ber[2]
  pfas_single$white[ii] <- race_med$ber[3]
  pfas_single$black[ii] <- race_med$ber[4]
  pfas_single$otherrace[ii] <- race_med$ber[5]
  pfas_single$lowinc[ii] <- income_med$ber[2]
  pfas_single$highinc[ii] <- income_med$ber[3]
  
  # Repeat for exposure
  pop_exp <- svyquantile(~exp_conc, design = nhanes_design, quantile=c(0.5), ci=TRUE)
  gender_exp <- svyby(~exp_conc, ~RIAGENDR,design=nhanes_design,svyquantile,quantile=c(0.5), ci=TRUE)
  age_exp <- svyby(~exp_conc, ~age_group,design=nhanes_design,svyquantile,quantile=c(0.5), ci=TRUE)
  race_exp <- svyby(~exp_conc, ~RIDRETH1,design=nhanes_design,svyquantile,quantile=c(0.5), ci=TRUE)
  income_exp <- svyby(~exp_conc, ~income_group,design=nhanes_design,svyquantile,quantile=c(0.5), ci=TRUE)
  
  pfas_single$popexp[ii] <- pop_exp$exp_conc[1]
  pfas_single$maleexp[ii] <- gender_exp$exp_conc[1]
  pfas_single$femexp[ii] <- gender_exp$exp_conc[2]
  pfas_single$youngexp[ii] <- age_exp$exp_conc[1]
  pfas_single$oldexp[ii] <- age_exp$exp_conc[2]
  pfas_single$mexexp[ii] <- race_exp$exp_conc[1]
  pfas_single$hispexp[ii] <- race_exp$exp_conc[2]
  pfas_single$whiteexp[ii] <- race_exp$exp_conc[3]
  pfas_single$blackexp[ii] <- race_exp$exp_conc[4]
  pfas_single$otherraceexp[ii] <- race_exp$exp_conc[5]
  pfas_single$lowexp[ii] <- income_exp$exp_conc[2]
  pfas_single$highexp[ii] <- income_exp$exp_conc[3]
  
  # Population ACC
  pfas_single$popacc[ii] <- pfas_single$acc[ii]
}
```

## Anlayze mixtures bioactivity:exposure ratios by survey demographic
```{r}
#Demographic data for 2009-2010 data
demo2009 <- read_xpt("./input/DEMO_F.XPT")
demo2009_wts <- read_xpt("./input/PFC_F.XPT")
nhanes_vars_c <- demo2009_wts %>% select(SEQN, WTSC2YR)
nhanes_vars <- demo2009 %>% select(SEQN,SDMVPSU,SDMVSTRA,RIAGENDR,RIDAGEYR,RIDRETH1,INDFMPIR)
for (ii in 1:11){
  test_df <- merge(pfas_combos$results[[ii]],nhanes_vars,by="SEQN")
  pfas_mix_demo <- merge(test_df,nhanes_vars_c,by="SEQN")
  # convert gender to factor
  pfas_mix_demo <- pfas_mix_demo %>%
                      mutate(RIAGENDR = recode(RIAGENDR, `1` = 0L,`2` = 1L))
  pfas_mix_demo$RIAGENDR <- as.factor(pfas_mix_demo$RIAGENDR)
  # convert age to factor
  # separate below 20 and above 20
  pfas_mix_demo <- pfas_mix_demo %>% mutate(age_group = ifelse(RIDAGEYR < 20, 0L, 1L))
  pfas_mix_demo$age_group <- as.factor(pfas_mix_demo$age_group)
  # convert ratio of family income to poverty to factor
  pfas_mix_demo <- pfas_mix_demo %>% mutate(income_group = ifelse(INDFMPIR<5, 1L, INDFMPIR))
  pfas_mix_demo <- pfas_mix_demo %>% mutate(income_group = ifelse(INDFMPIR==5, 2L, income_group))
  pfas_mix_demo <- pfas_mix_demo %>% mutate(income_group = ifelse(is.na(INDFMPIR), 0L, income_group))
  # use survey package to apply nhanes weights
  nhanes_design <- svydesign(id = ~SDMVPSU,
                             strata = ~SDMVSTRA,
                             weights = ~WTSC2YR,
                             nest = TRUE,
                             data = pfas_mix_demo)
  # population median analysis
  pop_med <- svyquantile(~ber, design = nhanes_design, quantile=c(0.5), ci=TRUE)
  # median analysis by survey demographics
  gender_med <- svyby(~ber, ~RIAGENDR,design=nhanes_design,svyquantile,quantile=c(0.5), ci=TRUE)
  age_med <- svyby(~ber, ~age_group,design=nhanes_design,svyquantile,quantile=c(0.5), ci=TRUE)
  race_med <- svyby(~ber, ~RIDRETH1,design=nhanes_design,svyquantile,quantile=c(0.5), ci=TRUE)
  income_med <- svyby(~ber, ~income_group,design=nhanes_design,svyquantile,quantile=c(0.5), ci=TRUE)

  # save median values
  pfas_combos$popmed[ii] <- pop_med$ber[1]
  pfas_combos$malemed[ii] <- gender_med$ber[1]
  pfas_combos$femmed[ii] <- gender_med$ber[2]
  pfas_combos$youngmed[ii] <- age_med$ber[1]
  pfas_combos$oldmed[ii] <- age_med$ber[2]
  pfas_combos$mexamer[ii] <- race_med$ber[1]
  pfas_combos$hispanic[ii] <- race_med$ber[2]
  pfas_combos$white[ii] <- race_med$ber[3]
  pfas_combos$black[ii] <- race_med$ber[4]
  pfas_combos$otherrace[ii] <- race_med$ber[5]
  pfas_combos$lowinc[ii] <- income_med$ber[2]
  pfas_combos$highinc[ii] <- income_med$ber[3]
  
  # repeat for exposure concentrations
  pop_exp <- svyquantile(~cM_tot, design = nhanes_design, quantile=c(0.5), ci=TRUE)
  gender_exp <- svyby(~cM_tot, ~RIAGENDR,design=nhanes_design,svyquantile,quantile=c(0.5), ci=TRUE)
  age_exp <- svyby(~cM_tot, ~age_group,design=nhanes_design,svyquantile,quantile=c(0.5), ci=TRUE)
  race_exp <- svyby(~cM_tot, ~RIDRETH1,design=nhanes_design,svyquantile,quantile=c(0.5), ci=TRUE)
  income_exp <- svyby(~cM_tot, ~income_group,design=nhanes_design,svyquantile,quantile=c(0.5), ci=TRUE)
  
  pfas_combos$popexp[ii] <- pop_exp$cM_tot[1]
  pfas_combos$maleexp[ii] <- gender_exp$cM_tot[1]
  pfas_combos$femexp[ii] <- gender_exp$cM_tot[2]
  pfas_combos$youngexp[ii] <- age_exp$cM_tot[1]
  pfas_combos$oldexp[ii] <- age_exp$cM_tot[2]
  pfas_combos$mexexp[ii] <- race_exp$cM_tot[1]
  pfas_combos$hispexp[ii] <- race_exp$cM_tot[2]
  pfas_combos$whiteexp[ii] <- race_exp$cM_tot[3]
  pfas_combos$blackexp[ii] <- race_exp$cM_tot[4]
  pfas_combos$otherraceexp[ii] <- race_exp$cM_tot[5]
  pfas_combos$lowexp[ii] <- income_exp$cM_tot[2]
  pfas_combos$highexp[ii] <- income_exp$cM_tot[3]
  
  # population median ACC
  pop_acc <- svyquantile(~acc_ca, design = nhanes_design, quantile=c(0.5), ci=TRUE)
  
  pfas_combos$popacc[ii] <- pop_acc$acc_ca[1]
 }

```

## Plot population BER
Represent distributions as boxplots and plot for each single chemical and mixture
```{r}
pfas_combos[c(12:15),] <- NA
pfas_combos$X1[c(12:15)] <- pfas_single$dtsxid
pfas_combos$popmed[c(12:15)] <- pfas_single$popmed
pfas_combos$results[c(12:15)] <- pfas_single$exposure
pfas_combos$mix_num[c(12:15)] <- c(12:15)

# names
for (jj in 1:nrow(pfas_combos)){
  name1 <- pfas_chems[pfas_chems$DSSTox_Substance_Id==pfas_combos$X1[jj],]$Substance_Name
  if (is.na(pfas_combos$X2[jj])){
    chem_name <- name1
  } else {
    name2 <- pfas_chems[pfas_chems$DSSTox_Substance_Id==pfas_combos$X2[jj],]$Substance_Name
    if (is.na(pfas_combos$X3[jj])){
      chem_name <- paste(name1, "+", name2)
    } else {
      name3 <- pfas_chems[pfas_chems$DSSTox_Substance_Id==pfas_combos$X3[jj],]$Substance_Name
      if (is.na(pfas_combos$X4[jj])){
        chem_name <- paste(name1, "+", name2, "+", name3)
      } else {
        name4 <- pfas_chems[pfas_chems$DSSTox_Substance_Id==pfas_combos$X4[jj],]$Substance_Name
        chem_name <- paste(name1, "+", name2, "+", name3, "+", name4)
      }
    }
  }
  pfas_combos$chem_name[jj] <- chem_name
}

# order from largest to smallest MOE median
plot_order <- order(pfas_combos$popmed, decreasing=TRUE)
# colors
plot_colors <- hcl.colors(16, palette = "Blues 3")

tiff("ber_population_dists_aeid132.tiff", units="in", width=15, height=11, res=600)
par(mar=c(15,8,2,1))
# plot first chemical
ii <- 1
test_df <- merge(pfas_combos$results[[plot_order[ii]]],nhanes_vars,by="SEQN")
pfas_mix_demo <- merge(test_df,nhanes_vars_c,by="SEQN")
nhanes_design <- svydesign(id = ~SDMVPSU,
                           strata = ~SDMVSTRA,
                           weights = ~WTSC2YR,
                           nest = TRUE,
                           data = pfas_mix_demo)
# median analysis
pop_med <- svyquantile(~ber, design = nhanes_design, quantile=c(0.5), ci=TRUE)

svyboxplot(~ber~1, nhanes_design, all.outliers=TRUE, ylab="BER", xlab=" ",main=" ", names=FALSE, log="y", at=c(1), xlim=c(0.5,15.5), ylim=c(40,20E4),col=c(plot_colors[17-ii]),cex.lab=2,cex.axis=1.5)

# add remaining chemicals to plot
for(ii in 2:15){
  test_df <- merge(pfas_combos$results[[plot_order[ii]]],nhanes_vars,by="SEQN")
  pfas_mix_demo <- merge(test_df,nhanes_vars_c,by="SEQN")
  nhanes_design <- svydesign(id = ~SDMVPSU,
                             strata = ~SDMVSTRA,
                             weights = ~WTSC2YR,
                             nest = TRUE,
                             data = pfas_mix_demo)
  svyboxplot(~ber~1, nhanes_design, all.outliers=TRUE,
             main=" ", add=TRUE, at=c(ii),col=c(plot_colors[17-ii]), cex.lab=2,cex.axis=1.5)
}
axis(1,at = c(1:15),labels=FALSE)
text(x=c(1:15),y=23,labels=c(pfas_combos$chem_name[plot_order]),srt=45,adj=1,xpd=NA,cex=1.5)
dev.off()


```

## Compare across demographic groups
Combine single chemical and mixture information to compare bioactivity:exposure ratio medians across demographic groups to the median population
```{r}

pfas_combos[c(12:15),] <- NA
pfas_combos$X1[c(12:15)] <- pfas_single$dtsxid
pfas_combos$popmed[c(12:15)] <- pfas_single$popmed
pfas_combos$femmed[c(12:15)] <- pfas_single$femmed
pfas_combos$malemed[c(12:15)] <- pfas_single$malemed
pfas_combos$youngmed[c(12:15)] <- pfas_single$youngmed
pfas_combos$oldmed[c(12:15)] <- pfas_single$oldmed
pfas_combos$mexamer[c(12:15)] <- pfas_single$mexamer
pfas_combos$hispanic[c(12:15)] <- pfas_single$hispanic
pfas_combos$white[c(12:15)] <- pfas_single$white
pfas_combos$black[c(12:15)] <- pfas_single$black
pfas_combos$otherrace[c(12:15)] <- pfas_single$otherrace
pfas_combos$lowinc[c(12:15)] <- pfas_single$lowinc
pfas_combos$highinc[c(12:15)] <- pfas_single$highinc
pfas_combos$mix_num[c(12:15)] <- c(1:4)

# names
for (jj in 1:nrow(pfas_combos)){
  name1 <- pfas_chems[pfas_chems$DSSTox_Substance_Id==pfas_combos$X1[jj],]$Substance_Name
  if (is.na(pfas_combos$X2[jj])){
    chem_name <- name1
  } else {
    name2 <- pfas_chems[pfas_chems$DSSTox_Substance_Id==pfas_combos$X2[jj],]$Substance_Name
    if (is.na(pfas_combos$X3[jj])){
      chem_name <- paste(name1, "+", name2)
    } else {
      name3 <- pfas_chems[pfas_chems$DSSTox_Substance_Id==pfas_combos$X3[jj],]$Substance_Name
      if (is.na(pfas_combos$X4[jj])){
        chem_name <- paste(name1, "+", name2, "+", name3)
      } else {
        name4 <- pfas_chems[pfas_chems$DSSTox_Substance_Id==pfas_combos$X4[jj],]$Substance_Name
        chem_name <- paste(name1, "+", name2, "+", name3, "+", name4)
      }
    }
  }
  pfas_combos$chem_name[jj] <- chem_name
}

pfas_heatmap <- data.frame(chem_name=pfas_combos$chem_name,
                           pop_med=pfas_combos$popmed,
                           Female=pfas_combos$femmed/pfas_combos$popmed,
                           Male=pfas_combos$malemed/pfas_combos$popmed,
                           Young=pfas_combos$youngmed/pfas_combos$popmed,
                           Old=pfas_combos$oldmed/pfas_combos$popmed,
                           Mexican=pfas_combos$mexamer/pfas_combos$popmed,
                           Hispanic=pfas_combos$hispanic/pfas_combos$popmed,
                           White=pfas_combos$white/pfas_combos$popmed,
                           Black=pfas_combos$black/pfas_combos$popmed,
                           Other_Race=pfas_combos$otherrace/pfas_combos$popmed,
                           LowIncome=pfas_combos$lowinc/pfas_combos$popmed,
                           HighIncome=pfas_combos$highinc/pfas_combos$popmed)
heatmap_add <- data.frame(chem_name=pfas_combos$chem_name,
                          pop_ber = pfas_combos$popmed,
                          female_ber=pfas_combos$femmed,
                          male_ber=pfas_combos$malemed,
                          young_ber=pfas_combos$youngmed,
                          old_ber=pfas_combos$oldmed,
                          mex_ber=pfas_combos$mexamer,
                          hisp_ber=pfas_combos$hispanic,
                          white_ber=pfas_combos$white,
                          black_ber=pfas_combos$black,
                          other_ber=pfas_combos$otherrace,
                          lowinc_ber=pfas_combos$lowinc,
                          highinc_ber=pfas_combos$highinc)
moe_order <- order(pfas_heatmap$pop_med, decreasing=TRUE)
pfas_heatmap <- pfas_heatmap[moe_order,]
heatmap_add <- heatmap_add[moe_order,]


pfas_info_plot1 <- melt(pfas_heatmap,
                        measure.vars=c("Female","Male","Young","Old","Mexican","Hispanic","White","Black","Other_Race","LowIncome","HighIncome"),
                        variable.name="demographic")
pfas_info_plot2 <- melt(heatmap_add,
                        measure.vars=c("female_ber","male_ber","young_ber","old_ber",
                                       "mex_ber","hisp_ber","white_ber","black_ber","other_ber","lowinc_ber","highinc_ber"),
                        value.name="ber")
pfas_demo_plot <- data.frame(pfas_info_plot1,ber=pfas_info_plot2$ber)

# Bubble plot to compare median BER values of survey demographic groups and median population BER
p1 <- ggplot(pfas_demo_plot, aes(x=demographic,y=factor(chem_name,unique(chem_name)),size=ber,fill=value))+
  geom_point(shape=21)+
  scale_size(range=c(3,12),name="Median BER: ",breaks=c(6E2,1E3,5E3,19.5E3))+
  scale_fill_gradientn(colours = c("red","white","midnightblue"),
                       values=rescale(c(min(pfas_demo_plot$value),1,max(pfas_demo_plot$value))),
                       limits=c(0.8,1.6),
                       oob=scales::squish,
                       name= TeX(r'($\frac{Group\, Median\, BER}{Population\, Median\, BER}: \; \;$)'))+
  theme_bw(base_size=20)+
  theme(axis.text.x = element_text(angle=50,hjust=1,vjust=1.0,size=14, color="black"),
        axis.text.y = element_text(size = 14,color="black"),
        axis.title = element_blank(),
        legend.text = element_text(size=14),
        legend.title=element_text(size=16),
        legend.position="bottom",
        legend.box = "vertical",
        legend.margin=margin(t=0,b=0),
        legend.key.width=unit(1.5,"cm"))+
  scale_x_discrete(labels=c("Female"="Female","Male"="Male",
                            "Young"="Age < 20 Years", "Old"= expression("Age">="20 Years"),
                            "Mexican"="Mexican American","Hispanic"="Other Hispanic",
                            "White"="Non-Hispanic White","Black"="Non-Hispanic Black",
                            "Other_Race"="Other Race",
                            "LowIncome"="Family Income:Poverty < 5","HighIncome"=expression("Family Income:Poverty">=5)))

# plot of median ACC values 
pfas_combos$popacc[c(12:15)] <- pfas_single$popacc
p2 <- ggplot(pfas_combos, aes(x=popacc,y=factor(chem_name,unique(chem_name))))+
  geom_point(size=3)+
  scale_x_log10(limits=c(10,60),labels = label_number(drop0trailing = TRUE))+
  theme_bw(base_size=20)+
  xlab(expression(paste("Median Pop. ACC [",mu, "M]")))+ 
  theme(axis.text.y = element_blank(),
        axis.ticks.y=element_blank(),
        axis.title.y = element_blank(),
        axis.title.x = element_text(size=14,margin = margin(t=-100)),
        panel.grid.major.x = element_blank(),
        panel.grid.minor.x = element_blank())

  
tiff("ber_bubbleplot_aeid132.tiff", units="in", width=12, height=10, res=800)
plot_grid(p1,p2,align="h",ncol=2, rel_widths=c(4/5,1/5))
dev.off()
```
